---
title: 'RMarkdown:  In Class Assignment'
author: "Jezel Valdez"
date: "Data 2401"
output: 
  html_document:
    toc: TRUE
    toc_depth: 3
---

```{r setup, include=FALSE}
# Everything in this chunk is R code. 
# You are not expected to understand or edit this yet. 
# We will talk about what this does in a later class, with a little preview in part 2.
knitr::opts_chunk$set(echo = TRUE) 
```

Reminders:

-   You do not need to memorize Markdown syntax.
-   You are expected to look things up using:
    -   RStudio’s Markdown Help
    -   Online documentation or examples
-   Click Knit as you go to check that your document still renders correctly.
-   Commit at the end, but consider committing as you go as well.

# Part 1: Markdown Practice

**Do not skip reading this instruction** Create a new section at the end of this section named "Your work here". In that section, complete the tasks below:

-   Make a *subsection* called Wise Words.
-   Put your favorite quote in a block quote.
-   Add a working, clickable link to a website that provides more information about that quote.
-   Make another *subsection* called "I recommend", and add some information about your favorite author or musician:
    -   A *subsubheading* with the name of the artist or author;\
    -   An example of their writing or lyrics (formatted in a *block of text*);\
    -   A *list* of things they have written or performed (remember to use the formatting markup for a list!), with any of the titles/names in bold.

### Your work here:

#### Wise words

*Float like a butterfly, sting like a bee.*

[- Muhammad Ali](https://www.thesportster.com/float-like-a-butterfly-sting-like-a-bee-meaning-and-orgin/)

#### I recommend

##### Beach House

> What comes after this, momentary bliss? Consequence of what you do to me.

###### Songs

-   Myth

-   PPP

-   Lazuli

-   Space Song

# Part 2: Code Chunks

```{r echo = FALSE}
2 + 2
```

Complete the following steps:

-   Knit the document and observe what appears in the output.
-   Change the chunk option echo=TRUE to echo=FALSE.
-   Knit the document again.
-   Finally, write 2–3 sentences answering the following questions:
    -   What changed between the two outputs?
    -   Did the calculation still run when the code was hidden?
    -   Why might someone want to hide code in a report?
    -   Why might someone want to show code in a report?

#### My work here:

From what I observed the only difference was that when i put 'echo = TRUE' the document that popped up showed 2+2 above the peice of code and the other didn't. The calculation did still run in the console even though it was hidden. Someone may want to hide it so it can be more visually appealing for non-coders to look at, but they may want to show it for coder's so they can see what is going on behind the scenes of the document.

# Part 3: A small R-in-markdown preview

-   Create a subsection within this section called About this document.
-   Write 2–3 sentences describing what this document is and what it produces.
-   Include one value generated by inline R code.

> To include inline code, use this weird little `r 2+2` pattern, putting the code where I have 2+2 (which is code!) You can use the function `Sys.Date()`, which would be added like this `r Sys.Date()` but you can do something else if you want. (Look at the knit html to see what this does.)

#### About this document

This document is an rmarkdown file that produces an HTML file when you knit it.

`r Sys.Date()`

# Submitting Instructions

When you are finished:

-   Knit the document so that it produces an html file.
-   Stage, commit, and push:
    -   The updated `.rmd` file
    -   The generated `.html` file
-   Submit the GitHub link to the assignment on Canvas.
